resistanceModelNotesAndy

### 2015-03-24 resistanceModelNotesAndy.Rmd
progress notes

**19/3/15** sat 10.15

@@

**22/3/15** mon 9.45-11.45 2hrs 5-6

@@

@@

1. look at modifying other parameters

1. start creating a shinyapp and/or vignette to help me understand how the model works

1. finish tidying documentation of reading in input vars in createInputMatrix() add avr names from runModel()
+ can use these later for roxygen doc of function inputs to resistSimple
+ and I could use find&replace to rename later if needed

1. check whether setting input[13,1] <- to the next line at 58 in createInputMatrix() was a bug

1. make it easier to run a single scenario and default scenarios
+ might do this by first adding a function rather than changing existing stuff
1. i think the main visual output is the frequency of resistance over time

1. the curtis fig2 plot is produced from >1 scenario, do I want to get it into 1 'reactive' scenario
1. put back in checks for things that should sum to 1
1. edit runModel carefully
1. check out the part about running sequential insecticide scenarios
1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.
1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. later, structure as R package, maybe move to a new github repo
1. re-look at R popgen packages when I've got more of a handle on what we are doing.

>>>>

**19/3/15** sat 10.15-2.15 4hrs

@@

**22/3/15** mon 9.45-11.45 2hrs 5-8 5hrs

@@

**23/3/15** tue 9.45-

created function to run shiny UI from package, and add it to readme

there was a bug that dominance had no effect, because I was setting `h.RS1_00` rather than `h.RS1_A0 & h.RS1_0B`

Cool! Seems to be working well now.

@@

1. create a vignette from first shiny app documenting how the model works

1. finish tidying documentation of reading in input vars in createInputMatrix()

1. the curtis fig2 plot is produced from >1 scenario, do I want to get it into 1 'reactive' scenario
1. put back in checks for things that should sum to 1
1. edit runModel carefully
1. check out the part about running sequential insecticide scenarios
1. start to write script to run sensitivity analysis, does it want to work by creating a large input.csv file, or by setting input object directly.
1. spend some time developing my understanding of how the model works
1. submit tilde bug report
1. re-look at R popgen packages when I've got more of a handle on what we are doing.
